Ownership types in theory and practice (in Rust)

### 2022-11-27 paper.tex
More writing progress

Potential solutions to the aliasing problem include banning aliases altogether, clearly advertising aliases or managing and controlling its effects\cite{ownership-types-survey}.
Many different flavours of ownership types have been explored.
In this paper, state of the art implementations of the general concept such as owners-as-dominators, owners-as-modifiers and owners-as-ombudsmen will be explored further.
These approaches differ in how much, if any, references/aliases they allow.

@@

\subsection{Owners-as-dominators}

One such flavour is the owners-as-dominators\cite{ownership-types-survey} invariant, where the heap is structured as a tree with each object being inside its owner.
External access is therefore only possible through the owner.

>>>>

Potential solutions to the aliasing problem include banning aliases altogether, clearly advertising aliases or managing and controlling its effects\cite{ownership-types-survey}.
Many different flavours of ownership types have been explored.
In this paper, state of the art implementations of the ownership type concept such as owners-as-dominators, owners-as-modifiers and owners-as-ombudsmen will be explored further.
These approaches differ in how what kind of, if any, aliases they allow.
\cite{ownership-types-survey}

@@

% TODO: second source to provide more detail of each owners-as-...
% TODO: find more varied words to classify these approaches as: principle, approach, model

\subsubsection{Owners-as-dominators}

One such flavour is the owners-as-dominators\cite{ownership-types-survey} invariant, where the heap is structured as a tree with each object being inside its owner.
External access is therefore only possible through the owner.
The rules that must be fulfilled for \emph{a} to validly reference \emph{b} are that either \emph{a} is owned by \emph{b}, \emph{a} and \emph{b} are siblings or \emph{b} is outside \emph{a}.
% TODO: more detail

The owners-as-dominators principle provides a simple, clear and strong guarantee, but makes programming more difficult by not allowing common idioms through aliasing.
\cite{ownership-types-survey}

\subsubsection{Owners-as-modifiers}

Another kind is the owners-as-modifiers model, which is a weaker form owners-as-dominators that additionally allows read-only references.
A read-only reference can only be used to read files and call pure methods, which may not modify any existing objects.
In essence, aliasing is unrestricted, but only the owner of an object can modify it.
If none of the rules that were specified for owners-as-dominators are adhered to, for \emph{a} to validly reference \emph{b} through reference \emph{r}, \emph{r} has to be a read-only reference and only pure methods can be called on it.
% TODO: more detail

The owners-as-modifiers principle expands the programming possibilities of the owners-as-modifiers principle and fulfills the requirements of verification of object-oriented programs.

\cite{ownership-types-survey}

\subsubsection{Owners-as-ombudsmen}

\cite{ownership-types-survey}
